%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Prafulla}{Chandra}{ 
\href{mailto:prafullachandra501@gmail.com}{prafullachandra501@gmail.com} | +91 8978127720
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{KL University}
\descript{Bachelor's Degree in Computer Science}
\descript{7.92 CGPA}
\location{June 2019 | Guntur, India}
\sectionsep

\subsection{TELANGANA BOARD OF}
\subsection{INTERMEDIATE EDUCATION}
\descript{95.8 percentile}
\location{May 2015 | Hyderabad, India}
\sectionsep

\subsection{Bhashyam Public School}
\descript{9.8 GPA}
\location{May 2013 | Hyderabad, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://www.facebook.com/chandra.prafulla}{\bf chandra.prafulla} \\
LinkedIn://  \href{http://linkedin.com/in/prafulla-chandra-04b7a511a}{\bf prafulla-chandra-04b7a511a} \\
Github://  \href{https://github.com/PrafullaChandraVedantam}{\bf PrafullaChandraVedantam} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{UNDERGRADUATE}
Data Structures and Algorithms\\
Object Oriented Programming\\
Database Management Systems\\
Operating Systems\\
File Structures\\
Computer Networks\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 10000 lines:}
VanillaJS, \textbullet{} C \textbullet{} Java \textbullet{} SpringBoot \textbullet{} 
Hibernate \\
\location{Databases}
\textbullet{} MySQL, OracleDB\\ 
\location{Academic Experience}
\textbullet{} C \textbullet{} C++ \textbullet{} Python\\
\location{Familiar}
\textbullet{} Apache Camel and Apache Kafka
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Cognizant}
\descript{| Programmer Analyst }
\location{Jun 2020 – Present | Kochi, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Working as a Java Full stack Developer , technologies include Spring MVC, Angular, Vaadin, Hibernate and Bootstrap
\end{tightemize}
\sectionsep

\descript{ Programmer Analyst Trainee }
\location{Jun 2019 – Jun 2020 | Hyderabad, India}
\begin{tightemize}
\item Worked with various java full stack technologies during my internship.
\end{tightemize}

\runsubsection{Axelta Systems Pvt. Ltd.}
\descript{ Intern }
\location{May 2017 – Jul 2017 | Hyderabad, India}
\begin{tightemize}
\item Built an automation product of lights and fans by
detecting the motion in the room using a PIR sensor to control appliances with relays.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Academic Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Projects}
\runsubsection{Fisherman app}\\
\descript{Safefy ensuring device}
\begin{tightemize}
\item Fisherman app is an application used near the coastal areas ,which ensures the safety of the tourists , fisherman who are into the waterbody. A watch-like device is connected to the app via LAN, which updates the heart beat levels, bp level,location of the person and sends an alert message to the guard outside the water body. 
\item TechStack used: Android Studio,Java, Arduino.
\end{tightemize}
\sectionsep

\runsubsection{Pixogram}\\
\descript{photo based social networking application}
\location{KL University}
\begin{tightemize}
\item The application allows users to upload photos to the service, which can be organized with tags and descriptions.
\item Users can follow and block other users. Users can also like photos, and follow other users to comment on their photos
\item TechStack used: Eclipse, Spring Boot, Jsp, Hibernate, MySQL .
\end{tightemize}
\sectionsep

\runsubsection{Online Education Portal}\\
\descript{A Mini Facebook}
\location{Built this as part of a college level expo}
\begin{tightemize}
\item This application allows admin to register students and faculty to a particular course and generate timetable
\item TechStack used:  Eclipse, SpringMVC, Jsp, Hibernate, OracleDB
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2018	     & top 52/2500  & Lead t KL Hack League\\
2014	     & Vice President  & SEA TechClub\\
2017     & 1st Prize & “OPEN INNOVATION HACKATHON” - UC BERKELEY\\
\end{tabular}
\sectionsep

\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}